---
title: "Portfolio Assignment 7"
author: "Shervin Kaandorp"
date: "16-5-2021"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dslabs)
library(tidyr)
```


## Lesson 7

### Portfolio Assignment 7

__7.1) Load the flu (“./data/flu_data.csv), the dengue (.”/data/dengue_data.csv) and the gapminder ({dslabs} package) into three separate dataframes in R.__

```{r download and import files}
download.file("https://raw.githubusercontent.com/DataScienceILC/tlsc-dsfb26v-20_workflows/main/data/flu_data.csv", destfile="data/flu.data.csv")

download.file("https://raw.githubusercontent.com/DataScienceILC/tlsc-dsfb26v-20_workflows/main/data/dengue_data.csv", destfile="data/dengue_data.csv")

flu_data <- read_csv("data/flu.data.csv", 
                     skip = 10)
dengue_data <- read_csv("data/dengue_data.csv",
                        skip = 11)
gapminder <- gapminder
```

__7.2) Check if they are in the right shape. Is the data in the ‘tidy’ format? If not change the format to ‘tidy’.__

```{r tidying flu and dengue}
flu_tidy <- flu_data %>% pivot_longer(matches(colnames(flu_data[2:30])), names_to="country", values_to ="flu_value")

dengue_tidy <- dengue_data %>% pivot_longer(matches(colnames(dengue_data[2:11])), names_to="country", values_to="dengue_value")
```

__7.3) Change the country and date variables of the three tables so that they coincide in terms of data type, class and values.__


